\bf Model Visualization Techniques for a Social Network Model

### 2018-09-12 paper-child.Rnw
forgot commit

In addition to assessing model fit, we are also interested in model behavior so that we can choose better fitting models in the future. We examine model behavior by visualizing collections of models. There are many possible ways to collect SAOMs together, so 
we chose four ways to create collections of models that would give us the most insight: (1) exploring the space of all possible models, (2) fitting the same model to the same data many times, (3) varying model settings, and (4) fitting the same model form to different data. We chose these four collections because they each explore something different about SAOMs. The first considers the many parameters to include in a SAOM, while the second results in different parameter estimates, so we can see how parameter estimates vary. The third collection shows how those many possible parameters affect the values of parameters in the fitted models. Finally, we explore how the same model behaves under two completely different circumstances.

>>>>

In addition to assessing model fit, we also want to learn about model behavior so that we can choose better fitting models in the future. We examine the behavior of SAOMs by visualizing collections of models. We build collections of models in four ways. First, we explore the space of all possible models to determine the most significant model parameters.  Second, we vary model settings to uncover relationships between parameters and their effects on the fitted model. Next, we fit the same model to the same data many times to assess the behavior of the underlying simulations. Finally, we fit the same model to different data to learn about fitted parameter values under different conditions. We chose these four collections because they each explore something different about SAOM behavior: the choice of parameters in the objective function, the effects of underlying simulations, and the resulting fitted values under different circumstances. Using the tools in our visualization toolbox, we %The first considers the many parameters to include in a SAOM, while the second results in different parameter estimates, so we can see how parameter estimates vary. The third collection shows how those many possible parameters affect the values of parameters in the fitted models. Finally, we explore how the same model behaves under two completely different circumstances.
